---
title: 'Week 11: Interpolation Problem Set'
author: 
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(PolynomF)
library(pracma)
```

## Problem 1.

Describe the difference between regression and interpolation. Provide a hand-drawn figure to illustrate. In the description, identify the following: - limitations to both - R tools available - best user practices

## Problem 2.

The following data describes a series of density measurements collected at a range of temperatures.

```{r}
Temp <- c(20,25,30,35,40,45)
Dens <- c(1.71,1.39,1.12,0.957,0.841,0.771)
knitr::kable(data.frame(Temp, Dens), col.names = c("Temp [&deg;F]", "Density [kg m^-3^]"))
```

Imagine you were given the table above and you did not have R. Use the linear interpolation equation to estimate density at 32.9°F. (Do your calculations in the chunk below).

```{r}

```

Now using R functions show the resulting plots for linear, spline, nearest, and constant interpolation.

```{r}

```

For this dataset, what method would you recommend?

## Problem 3.

In engineering applications, steam tables are often used to determine thermodynamic properties of water and steam at various temperatures and pressures. You are tasked with interpolating values from a steam table to find the specific enthalpy of water at a given temperature using interpolation.

A steam table is provided for saturated water by temperature in the data folder.

```{r}
steam <- read_csv(file = "data/saturated_by_temperature_V1.5.csv", skip = 6)
```

Using linear interpolation, what is the enthalpy of liquid water at 370.5 °C?

```{r}

```

What method of interpolation would improve upon this interpolated estimate? Use this method to improve upon your linear estimate

```{r}

```
